---
author: "Arthur Pere"
date: '`r invisible( Sys.setlocale("LC_TIME", "C") ); format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    number_sections: yes
    theme: united
    toc: yes
    toc_depth: 5
    toc_float: yes
title: "Report BIOMASS"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, comment = NA, fig.align = "center")
```
```{r,message=FALSE,warning=FALSE}
library(knitr)
setwd("~/Bureau/document arthur/Analyse TMFO")
```


# Load data
```{r load data, message=FALSE}
if (!require(BIOMASS)) devtools::install_github("AMAP-dev/BIOMASS")
devtools::load_all("~/Bureau/document arthur/biomass/")
library(data.table)
library(ggplot2)
library(proj4)

# Read data
dataTene <- fread("data_Tene_FOS.csv", dec = ",")

# Recompute relative coordinates at the plot level (coordinates were originally set over the whole experimental design).
dataTene[, ":="(XRel = x - min(x, na.rm = T), YRel = y - min(y, na.rm = T)), by = plot ]

# DBH in mm to cm
dataTene[, dbh := dbh / 10]

# read the coordinates
dataTeneCoord <- fread("Tene_Coord_FOS.csv")

# Get Feldpausch regions
dataTeneCoord[, Feldregion := computeFeldRegion(cbind(longitude, latitude))]
dataTene[unique(dataTeneCoord, by = "Plot"),
  on = c("plot" = "Plot"), ":="(regionFeld = i.Feldregion)
] # Assign a Feldpausch region to all trees


# set the corners
dataTeneCoordUTM <- setDT(dataTeneCoord[, numberCorner(longlat = cbind(longitude, latitude), plot = Plot, origin = (corner == 2), clockWise = T)])

dataTeneCoordUTM[ , codeUTM := dataTeneCoord[, latlong2UTM(cbind(longitude, latitude))]$codeUTM]

# Divide plots into 100*100 m2 subplots
dataTenecut <- setDT(dataTeneCoordUTM[, cutPlot(cbind(X, Y), corner = corner, plot = plot, gridsize = 50, dimX = 200, dimY = 200)])

dataTenecut[unique(dataTeneCoordUTM, by = "plot"), on = "plot", codeUTM := i.codeUTM]

# Assign trees to subplots
dataTene[, subplot := attributeTree(cbind(XRel, YRel), plot, dataTenecut)]


# Assign the lat-long coordinates of the plot center to all trees
dataTene[dataTeneCoord[, .(lat = mean(latitude), long = mean(longitude)), by = Plot][, .(plot = Plot, lat, long)],
  on = "plot",
  ":="(lat = i.lat, long = i.long)
]

# read tree heigth measurements for a subset of trees
dataTeneHeigth <- fread("Tene_height_FOS.csv", dec = ",")

```

# Location of the plots  
```{r Localisation of the plot, echo=FALSE, message=FALSE, warning=F}
lat.long <- unique(dataTeneCoord[, .(longitude, latitude)])
require("ggmap")
mp <- NULL
mapWorld <- borders("world", colour = "gray50", fill = "gray50") # create a layer of borders
mp <- ggplot() + mapWorld
mp <- mp + geom_point(data = lat.long, aes(x = longitude, y = latitude), color = "red", size = 2)
mp
```



# Retrieve wood density
```{r correctTaxo, include=FALSE}
correctTaxonomy <- correctTaxo(genus = dataTene$genus, species = dataTene$species)
dataTene[, ":="(genusCorrected = correctTaxonomy$genusCorrected,
  speciesCorrected = correctTaxonomy$speciesCorrected)]
rm(correctTaxonomy)
```
```{r Retrieve wood density, message=FALSE}
# retrieve the wood density and bring it in the data base
dataWD <- getWoodDensity(
  genus = dataTene$genusCorrected,
  species = dataTene$speciesCorrected,
  stand = dataTene$plot
)
dataTene[, WD := dataWD$meanWD]
dataTene[, sdWD := dataWD$sdWD]
```
```{r include=FALSE}
levelswd <- 100 * table(dataWD$levelWD) / length(dataWD$levelWD)
```
**Overall, `r round(levelswd["species"],1)` % of the values have been attributed at the species level, `r round(levelswd["genus"],1)` % at the genus level, and `r round(100-sum(levelswd[c("species","genus")]),1)` % at the plot level.**



# Construct H-D models




```{r Construct HD model, message=FALSE}
result <- modelHD(dataTeneHeigth$dbh, dataTeneHeigth$Height)
method <- result$method[ which.min(result$RSE) ] # Select the method for which the RSE is the minimun
```

```{r echo=FALSE}
kable(result, row.names = F, caption = "Comparison of the different methods")
```





We implemented a `r method` model of the form:

`r if(method != "log1") {"<!--"}`
$$ H = exp(a + b \cdot log(D)) $$
`r if(method != "log1") {"-->"}`

`r if(method != "log2") {"<!--"}`
$$ H = exp(a + b \cdot log(D) + c \cdot log(D)^2) $$
`r if(method != "log2") {"-->"}`

`r if(method != "log3") {"<!--"}`
$$ H = exp(a + b \cdot log(D) + c \cdot log(D)^2 + d \cdot log(D)^3) $$
`r if(method != "log3") {"-->"}`

`r if(method != "michaelis") {"<!--"}`
$$ H= a \cdot \dfrac{D}{b+D} $$
where *a* represents the asymptotic height of trees in the stand.
`r if(method != "michaelis") {"-->"}`


`r if(method != "weibull") {"<!--"}`
$$H=a  \cdot (1-exp(-(D/b)^c))$$
where *a* represents the asymptotic height of trees in the stand.
`r if(method != "weibull") {"-->"}`







```{r, echo=FALSE}
HDmodel <- modelHD(dataTeneHeigth$dbh, dataTeneHeigth$Height, method = method)
kable(cbind(t(HDmodel$coefficients[, 1]), RSE = HDmodel$RSE),
  digits = 3,
  caption = paste(HDmodel$method, "model parameters of the H-D relationship among plots")
)
```

# Retrieve the heigth of trees
```{r, warning=FALSE}
# Using the model HD
dataTene[, c("Hlocal", "RSElocal") := retrieveH(dbh, model = HDmodel)] # retrieve heigth with the local HD model
dataTene[, c("Hfeld", "RSEfeld") := retrieveH(dbh, region = unique(regionFeld)), by = regionFeld] # retrieve heigth with Feldpausch's HD models
dataTene[, c("Hchave", "RSEchave") := retrieveH(dbh, coord = cbind(long, lat))] # retrieve heigth with Chave's HD model
```
```{r echo=FALSE, warning=F}

ggplot(
  data = melt(dataTene, id.vars = "dbh", measure.vars = c("Hlocal", "Hfeld", "Hchave"), variable.name = "Method"),
  aes(x = dbh, y = value, lty = Method, color = Method)
) + geom_line() +
  labs(title = "Comparison of the methods for retrieving tree height", x = "dbh", y = "H") +
  scale_color_discrete(labels = c("Local", "Feldpausch", "Chave")) +
  scale_linetype_discrete(labels = c("Local", "Feldpausch", "Chave"))

```

# Estimating biomass and associated uncertainties

Below, we used a Bayesian Monte-Carlo scheme to estimate the mean AGB and associated credibility interval per plot.

## Using a local H-D model

```{r global model, message=FALSE, warning=FALSE}
resultAGB <- AGBmonteCarlo(
  D = dataTene$dbh,
  WD = dataTene$WD,
  errWD = dataTene$sdWD,
  H = dataTene$Hlocal,
  errH = unique(dataTene$RSElocal),
  Dpropag = "chave2004"
)

ResHDlocal <- setDT(summaryByPlot(AGB_simu = resultAGB$AGB_simu, plot = dataTene$subplot))
```


```{r, echo=F}
kable(ResHDlocal, row.names = F, caption = "AGB estimates per plots using the local H-D model", label = "tab:AGB_local", digits = 1)
```


## Using Chave et al. 2014 Equation 7 model
```{r Chave model}
resultAGB <- AGBmonteCarlo(
  D = dataTene$dbh,
  WD = dataTene$WD,
  errWD = dataTene$sdWD,
  coord = dataTeneCoord[1, .(longitude, latitude)],
  Dpropag = "chave2004"
)
ResHDChave <- setDT(summaryByPlot(AGB_simu = resultAGB$AGB_simu, plot = dataTene$subplot))
```

```{r, echo=F}
kable(ResHDChave, row.names = F, caption = "AGB estimates per plots using the Chave method", label = "tab:AGB_local", digits = 1)
```


## Using Feldpausch et al. 2012 regional Weibull models
```{r Feldpaush, message=FALSE, warning=FALSE}
resultAGB <- AGBmonteCarlo(
  D = dataTene$dbh,
  WD = dataTene$WD,
  errWD = dataTene$sdWD,
  H = dataTene$Hfeld,
  errH = unique(dataTene$RSEfeld),
  Dpropag = "chave2004"
)

ResHDregion <- setDT(summaryByPlot(AGB_simu = resultAGB$AGB_simu, plot = dataTene$subplot))
```

```{r, echo=FALSE}
kable(ResHDregion, row.names = F, caption = "AGB estimates per plots using Feldpaush et al. 2012 H-D models", digits = 1)
```


```{r Calculating the maximum height and the Loreys height per (sub)plot, message=F, warning=F}
# Max height by subplot
maxH <- dataTene[, .(
  Hlocal = max(Hlocal, na.rm = T),
  Hfeld = max(Hfeld, na.rm = T),
  Hchave = max(Hchave, na.rm = T)
), by = subplot ]

# Compute the Lorey height
dataTene[, BAm := (pi * (dbh / 2)^2) / 10000 ]

dataTene[, ":="(HBAlocal = Hlocal * BAm, HBAfeld = Hfeld * BAm, HBAchave = Hchave * BAm)]
Lorey <- dataTene[, .(
  LoreyLocal = sum(HBAlocal, na.rm = T) / sum(BAm, na.rm = T),
  LoreyFeld = sum(HBAfeld, na.rm = T) / sum(BAm, na.rm = T),
  LoreyChave = sum(HBAchave, na.rm = T) / sum(BAm, na.rm = T)
), by = subplot]

# mean of wood density by subplot
meanWD <- dataTene[, .(meanWD = mean(WD, na.rm = T)), by = subplot]
```



# Comparison of the AGB approaches

```{r,fig.width=8, fig.height=5,echo=F}
order <- ResHDlocal[, order(AGB)]
ResHDlocal <- ResHDlocal[order, ]
ResHDregion <- ResHDregion[order, ]
ResHDChave <- ResHDChave[order, ]

xcoordinate <- 1:nrow(ResHDlocal)

plot(xcoordinate, ResHDlocal$AGB,
  pch = 20, cex = 1.5, axes = F, xlab = "", ylab = "", col = "blue",
  ylim = c(0, max(ResHDlocal$Cred_97.5, ResHDregion$Cred_97.5, ResHDChave$Cred_97.5)),
  main = "Comparison of the AGB approaches", cex.main = 1.2
)

segments(xcoordinate, ResHDlocal$Cred_2.5, xcoordinate, ResHDlocal$Cred_97.5, lwd = 2, col = "blue")
lines(xcoordinate, ResHDregion$Cred_2.5, lty = 1, col = "red")
lines(xcoordinate, ResHDregion$Cred_97.5, lty = 1, col = "red")
lines(xcoordinate, ResHDChave$Cred_2.5, lty = 2, col = "grey20")
lines(xcoordinate, ResHDChave$Cred_97.5, lty = 2, col = "grey20")
axis(side = 1, at = xcoordinate, labels = ResHDlocal$subplot)
axis(side = 2, at = seq(0, ceiling(max(ResHDlocal$AGB, ResHDregion$AGB, ResHDChave$AGB) + 2000), 100), las = 1)
legend("topleft", c("Local HD", "Feldpausch", "Chave"),
  col = c("blue", "red", "grey20"),
  bg = "white", lty = c(0, 1, 2), pch = c(20, -1, -1)
)
```




# Preparing the outputs

```{r,echo=T,message=FALSE}

#### Prepare the 
dataTenecut[ , c("long", "lat") := project(.(XAbs, YAbs), proj = unique(.BY), inverse = T), by = codeUTM ]
dataTenecut[, ':='("Lat_cnt" = mean(lat), "Long_cnt" = mean(long)), by = subplot]

ResTot = rbindlist(lapply(split(dataTenecut, by = "subplot", keep.by = T), function(data){
  name = c("Lat_sw", "Lon_sw", "Lat_nw", "Lon_nw", "Lat_se", "Lon_se", "Lat_ne", "Lon_ne")
  
  v = as.vector( t(data[order(corner), .(lat, long)]) )
  names(v) = name
  v = as.list(v)
  
  v[["subplot"]] = data$subplot[1]
  v[c("subplot", name)]
}))

ResTot[unique(dataTenecut, by = "subplot"), on = "subplot", 
       ':='("Lat_cnt" = i.Lat_cnt, "Long_cnt" = i.Long_cnt)]

# Merge the result of AGB from HD local by subplot
ResTot[ResHDlocal, on = c(subplot = "plot"), ":="(AGB_local = i.AGB)]

# Merge maximum of the heigth of the trees given for each HD models by subplot
ResTot[maxH, on = "subplot", ":="(H_max_Local = i.Hlocal)]

# Merge the Lorey heigth given for each HD models by subplot
ResTot[Lorey, on = "subplot", ":="(H_Lorey_local = i.LoreyLocal)]

# write the file
fwrite(ResTot, file = "data_AGB.csv", sep = "\t")
```
